Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 introduction.tex
In latency list, changed 'calculating pointings' to 'calculating telescope pointings'
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1225 ccdd05d5-56c1-461a-bf98-85f6876523b4

\paragraph{Alert generation (2--3~min)}%
S6/VSR3 saw the introduction of low-latency astronomical
alerts, which required gathering event parameters and sky localization from the
various online analyses, downselecting the events, and calculating pointings.
If other sources of latency improve, the technical latency associated with this
infrastructure could dominate, so work should be done to improve it.

>>>>

\paragraph{Alert generation (2--3~min)}%
S6/VSR3 saw the introduction of low-latency astronomical
alerts, which required gathering event parameters and sky localization from the
various online analyses, downselecting the events, and calculating telescope pointings.
If other sources of latency improve, the technical latency associated with this
infrastructure could dominate, so work should be done to improve it.
